SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2021-01-16 maintex.tex
updated Results section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
\caption[]{(\textbf{Top}) Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic). From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line. (\textbf{Bottom}) BPT diagram for the MaNGA galaxies. }
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18),
\end{equation}
Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog. We further apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}. \textbf{This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in the centers of our galaxies.} Finally, we use the BPT diagnostic \citep{Baldwin:1981} to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch. \textbf{}

@@

@@

From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets. After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. This give us a total of \textbf{169} close pairs.

@@

In the second method, we select a ``tailored'' control sample for each paired galaxy from the full sample of isolated galaxies. We select a subsample of 20 control galaxies for each paired galaxy. We first select all of the control galaxies which are within a 0.1~dex stellar mass limit and within the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. Since the MaNGA sample has a tight distribution in stellar mass and redshift, the stellar mass and MaNGA subsample restriction effectively sets a $\Delta z$ $\lesssim$ $\sim$0.025 redshift tolerance. With these requirements, most paired galaxies will find between 20$-$100 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20. A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found. Only 5 of the paired galaxies required an extra iteration to find 20 controls.

@@

We measure the SFR from the extinction corrected H$\alpha$ luminosity, $L_{{\rm H}\alpha}$. We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination: 
\begin{equation}\label{eq:sfr}
\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}.
\end{equation}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{fig/ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) \textbf{extracted from a 0.5\reff\ aperture}. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the \textbf{169} paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.

The difference profiles are shown to be centrally enhanced by $\sim$0.25 $\pm$ 0.1 dex. Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.15$-$0.25 dex higher than the sample average.

The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex. The paired galaxies in the mass range, \logm\ $=$ 9.0$-$9.5, feature enhanced sSFR in their disks of 0.1$-$0.2 dex. As we will show in the next section, \S~\ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.

To understand why these high mass galaxies behave differently from the rest of the sample, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}. The whole sample has a v-shaped separation distribution. This is the result of the combination of the two different samples, the inside-IFU and outside-IFU samples. The outside-IFU sample should find more pairs at wide projected separations due to the larger volume to find companions in. The separation distribution of the inside-IFU sample is limited by MaNGA's IFU sizes and the sample's redshift distribution; the maximum possible projected separation for a MaNGA target with $z$ $=$ 0.15 and a 127 spaxel IFU is about 40 kpc. The highest mass galaxies in the sample are at closer projected separations in comparison to the rest of the sample with 70\% of the highest mass galaxies being within 20 kpc. As we will show in \S~\ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.

@@

The mass ratio here is defined as, 
\begin{equation}
\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
\end{equation}
where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of \textbf{its identified} companion galaxy. \textbf{We not only use the mass ratio to study how a major merger behaves differently from a minor merger but also to study how the more massive galaxy of a pair behaves differently from the less massive galaxy of the pair. We expect that either component of a similar mass pair will behave in a similar fashion; however, in a minor merger the large central galaxy may not respond to the merger event in the same way than its companion dwarf galaxy. The two different scenarios can be differentiated with our definition of the mass ratio; when the MaNGA target is the more massive companion of the pair, its mass ratio is positive and when MaNGA target is the less massive companion of pair the mass ratio is negative.}

%{\it In the sample, the MaNGA target is not always the more massive component of the pair. We split the sample into two groups based on their mass ratios; primary companions in which the MaNGA target is the more massive galaxy and secondary companions in which the MaNGA target is the less massive galaxy.}

For the outside-IFU pair sample we use the stellar masses enclosed by the $r$-band elliptical Petrosian apertures from the NSA catalog. The inside-IFU pair sample is left out of this analysis, because most of the secondary companions in these pairs are missing in the NSA catalog and the \citet{Simard:2011} catalog.

In \textbf{left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins; the primary and secondary companion of a major merger, $|\Delta$log($M$)$|$ $<$ 0.5, and the primary and secondary companion of a minor merger, $|\Delta$log($M$)$|$ $>$ 0.5. Regardless of the mass ratio, the centers of the paired galaxies are centrally enhanced, though major mergers have stronger enhancements in their centers by $\sim$0.2 dex over minor mergers. Secondary companions also feature slightly higher levels of enhancement in their centers than primary companions at the same mass ratios by $\sim$0.1 dex.

The sSFR offsets in the outskirts of the galaxy pairs show a dependence on the mass ratio. Primary companions show a zero to positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts. Secondary companions feature a suppression to the sSFR in their outskirts of about 0.1$-$0.4 dex.

In \textbf{right panel} of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0). These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0. We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.

@@

This effect can be seen more clearly in the plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation. The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc. While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex. Within 20 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex. Our data shows that the sSFR enhancement persists out to at least $r_{\rm p} = 50$~kpc, which is the limit of our pair selection. In the next section, we will compare our results with those from previous studies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with Previous Work}\label{sec:disc}

\subsection{Difference Radial Profiles}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile as a function of galactocentric radius between our work and previous works. The post-merger galaxies in \citet{Thorp:2019} have sSFR enhancements between $\sim$0.05$-$0.2 dex higher than our sample of paired galaxies. The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(sSFR) $=$ 0.5, roughly 0.25 dex higher than our paired galaxies. The post-merger galaxies also feature enhanced sSFR in their disk past 1.0 \reff\ of $\sim$0.1$-$0.15 dex. The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.

The galaxy pairs in \citet{Pan:2019} have sSFR enhancements that are roughly $\sim$0.1$-$0.2 dex higher than our sample. Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks. The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of post-merger galaxies while our sample has no post-merger galaxies. These post-merger galaxies are predicted to have higher levels of star formation over other paired galaxies due to a second larger burst of star formation which is triggered as the merging galaxies coalesce and may be able to increase the sample's average sSFR enhancement.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=\linewidth]{fig/bpt-cmd.pdf}
\caption[]{(\textbf{Left}) Color-magnitude diagram for MaNGA galaxies. The grey circles represent the whole MaNGA sample and the color scale reflects the local density around each data point in this color-magnitude plane, as indicated by the color bar on the top. The {\it blue} diamonds represent the star forming paired galaxies (by the BPT and \ewha\ cuts), the {\it red} diamonds represent the paired galaxies which are classified as retired (by the \ewha\ cut), and the {\it green} diamonds represent the paired galaxies containing an AGN (as identified by the BPT diagnostic). From top to bottom, the dashed lines divide the sample into red sequence, green valley, and blue cloud. The star-forming galaxy sample used in this paper are the galaxies below the lower dividing line. (\textbf{Center}) BPT diagram for the MaNGA galaxies. (\textbf{Right}) The WHAN diagram for the MaNGA galaxies. }
\label{fig:cmd}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{equation}\label{eq:blue}
NUV-r = 3.1682 - 0.16 (\mathcal{M}_{\rm i}+18)
\end{equation}
\begin{equation}\label{eq:red}
NUV-r = 4.7866 - 0.04 (\mathcal{M}_{\rm i}+18),
\end{equation}
Where $NUV-r$ is the color from SDSS's $k$-corrected absolute magnitude and $\mathcal{M}_{\rm i}$ is the $i$-band magnitude from the NSA catalog.

We use the BPT diagnostic \citep{Baldwin:1981}, shown in the center of Figure \ref{fig:cmd}, to remove galaxies with possible AGN in their centers. Specifically, we use the emission line ratios, log([O~{\sc iii}]/H$\beta$) and log([N~{\sc ii}]/H$\alpha$), extracted from a 1.3~kpc aperture along with the maximum starburst line of \citet{Kewley:2001} as the demarcation between the star-forming branch and the AGN branch.

\textbf{Based on the WHAN diagram, shown in the right panel of Figure \ref{fig:cmd}, we apply an \ewha\ $\ge$ \textbf{6\AA} cut on galaxy spectra extracted from a 1.0~\reff\ aperture to ensure that all \textbf{retired} galaxies are removed from the sample \citep{Cid-Fernandes:2011}.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{deluxetable*}{cccccccccc}
%\tablestypesize{\small} \tablewidth{0pt}
\tablecaption{Pair Catalog}
\tablehead{
\colhead{Plate} & \colhead{IFU} & \colhead{Sample} & \colhead{\Delta\theta} & \colhead{r_{\rm p}} & \colhead{\Delta \rm{log}(M)} & \colhead{R.A.} & \colhead{Decl.} & \colhead{Redshift} & \colhead{log(M)} \\
\colhead{} & \colhead{} & \colhead{} & \colhead{(arcseconds)} & \colhead{(kpc)} & \colhead{(dex)} & \colhead{(deg)} & \colhead{(deg)} & \colhead{} & \colhead{log(M_\odot)} \\
\colhead{(1)} & \colhead{(2)} & \colhead{(3)} & \colhead{(4)} & \colhead{(5)} & \colhead{(6)} & \colhead{(7)} & \colhead{(8)} & \colhead{(9)} & \colhead{(10)}
}
\decimals
\startdata
7443 & 12703 & 1 & 7.3 & 5.8 & 0.0 & 229.52558 & 42.74584 & 0.04027 & 10.8 \\
7960 & 12703 & 1 & 78.2 & 39.0 & 1.2 & 259.22831 & 31.52755 & 0.02475 & 10.1 \\
7964 & 3704 & 1 & 55.0 & 19.7 & 1.7 & 316.25170 & -0.93328 & 0.01759 & 9.2 \\
7975 & 12704 & 2 & 2.9 & 4.9 & 0.6 & 324.58642 & 11.34867 & 0.08886 & 11.1 \\
7977 & 9102 & 2 & 8.6 & 10.5 & 2.1 & 332.83066 & 12.18472 & 0.06309 & 10.8 \\
8078 & 6104 & 2 & 30.1 & 26.2 & -0.1 & 42.73943 & 0.36941 & 0.04421 & 10.1 \\
8078 & 12703 & 1 & 35.4 & 20.0 & 0.9 & 42.57027 & 0.09199 & 0.02808 & 10.8 \\
8079 & 1902 & 1 & 7.3 & 3.1 & 1.5 & 42.54777 & -0.99910 & 0.02129 & 9.5 \\
8079 & 12702 & 1 & 61.7 & 27.4 & -0.6 & 41.86858 & -0.26820 & 0.02198 & 10.3 \\
8080 & 9101 & 2 & 11.0 & 9.7 & 0.0 & 47.34003 & -0.40794 & 0.04482 & 9.9 \\
\enddata
\tablecomments{
(1) MaNGA Plate number; (2) MaNGA IFU ID; (3) subsample flag: 1-Primary Sample, 2-Secondary sample; (4-5) projected separation in arcseconds and kiloparsecs; (6) mass ratio, (7-8) right ascension and declination in degrees; (9) redshift; (10) stellar mass. \\ \\
(This table is available in its entirety in a machine-readable form in the online journal. A portion is shown here for guidance regarding its form and content.)
}
\label{tab:pair}
\end{deluxetable*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

From the NSA catalog's 641,409 galaxies, we find 492 galaxies which are paired to MaNGA targets. After restricting the sample to SFGs, we have another 133 MaNGA targets with paired galaxies outside of the IFU. MaNGA targets which have both an inside-IFU and an outside-IFU pair are left to the inside-IFU sample. This gives us a total of \textbf{169} close pairs, shown in Table \ref{tab:pair}.

@@

In the second method, we select a ``tailored'' control sample for each paired galaxy from the full sample of isolated galaxies. We select a subsample of 20 control galaxies for each paired galaxy. We first select all of the control galaxies which are within 0.1 dex in stellar mass limit, \textbf{0.025 in redshift, 20\% \reff}, and within the same MaNGA subsample (e.g. Primary or Secondary) as the paired galaxy. With these requirements, most paired galaxies will find between 20$-$100 control galaxies. Since we want each paired galaxy to be treated in a similar manner, we randomly down-select the total number of acquired control galaxies to 20. A given control galaxy may be selected for multiple pairs by the pipeline; most of the control galaxies are used at least once and the average number of times a given control is reused is between 4$-$6 times. In the cases where a paired galaxy does not initially acquire 20 control galaxies we iteratively expand the stellar mass limit by 0.1 dex until at least 20 control galaxies are found. Only 5 of the paired galaxies required an extra iteration to find 20 controls.

@@

We measure the SFR from the extinction corrected H$\alpha$ luminosity, $L_{{\rm H}\alpha}$. We use the SFR formula, Equation \ref{eq:sfr}, from \citet{Murphy:2011} which uses a Kroupa IMF, Solar metallicity, a constant SFR at an age of 100 Myr, and Case-B recombination: 
\begin{equation}\label{eq:sfr}
\frac{\rm{SFR}}{M_{\odot} \, \rm{yr^{-1} kpc^{-2}}} = \frac{L_{\rm H\alpha}}{1.86 \times 10^{41}\, \rm{erg\,s}^{-1}}.
\end{equation}

@@

\textbf{
We also restrict the used spaxels to those with \ewha\ $\ge$ 6 \AA\ to remove retired regions from the survey \citep{Cid-Fernandes:2011}. This effectively sets -10.8 yr$^{-1}$ as the lower limit to the sSFR in our galaxies.
}

@@

\textbf{ 
We repeat this analysis for the \ewha\ in Figure \ref{fig:ewha_prof}. We find that the \ewha\ profiles are in close agreement with the sSFR profiles, which shows that we can be confident of {\sc SPFIT}'s measurement of the sSFR. We do see that the pair-control offsets are lightly suppressed using the \ewha. 
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{fig/ssfr_mass.pdf}
\caption[]{The \textbf{Left} panel shows the $\Delta$log(sSFR) profiles where the difference profiles are constructed from the difference between the paired galaxy profiles and a set of 20 control galaxies. The profiles are split into five different stellar mass bins and the highlighted region about the profiles represent the standard error of mean of the profile. The black dashed line represents the mean profile between the four difference mass ranges. The number of paired galaxies in each mass range is given in the legend in parentheses. The \textbf{Right} panel shows the nuclear $\Delta$log(sSFR) \textbf{extracted from a 0.5\reff\ aperture}. The black squares are the mean values within a stellar mass bin (where the size of the bins are shown the the horizontal error bars). The vertical error bars on the black squares represent the standard deviation within the bin. The horizontal, dashed black line represents the median central enhancement of the pair sample. Galaxies in the outside-IFU (Blue) and inside-IFU (Red) samples are separately depicted.
}
\label{fig:ssfr_mass}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Tailored-Controls Difference Profiles}\label{sec:tailored}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{fig/ssfr_dm.pdf}
\caption[]{Same as Figure \ref{fig:ssfr_mass} except the difference profiles are split by the mass ratio of the pair. The \textbf{top} row is the absolute value of the mass ratio and the \textbf{bottom} row is the plain mass ratio. Taking the mass ratio without the absolute value allows us to separately study the more massive companions of pairs from less massive companions from pairs. The inside-IFU sample is left out of this analysis because we do not yet have reliable measurements of their total stellar mass ratios.}
\label{fig:ssfr_dm}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the second method, we match each paired galaxy to a set of 20 control galaxies of similar stellar masses and redshifts, as described in \S~\ref{sec:control}. We then take the median of the azimuthally averaged profiles of the tailored control sample. Finally, we obtain the $\Delta\log$sSFR profile for each of the \textbf{169} paired galaxies by calculating the difference between its sSFR profile and the median profile of its control sample.

@@

\textbf{To focus on the sSFR offsets in the centers of the galaxies, we also calculate the sSFR difference between each paired galaxy and its control sample in the central 0.5~\reff. The central sSFR is calculated for each galaxy by taking spaxels within 0.5 \reff\ and whose H$\alpha$ flux has S/N $\ge$ 3 and then taking the median value of sSFR of the selected spaxels. Once this is done we calculate the $\Delta$log(sSFR) using the same method as the $\Delta$log(sSFR) radial profiles are made. The central sSFR of a paired galaxy is compared against the sSFR of a set of 20 similar control galaxies, the same set of controls which were used for the $\Delta$log(sSFR) profiles, by taking the difference between the central sSFR of the paired galaxy and the median sSFR of the 20 selected control galaxies. We depict the central $\Delta$log(sSFR) as a function of stellar mass in the right hand panel of Figure \ref{fig:ssfr_mass}.}

The difference profiles are shown to be centrally enhanced by $\sim$0.3 $\pm$ 0.1 dex. Similar to what was seen in \S~\ref{sec:mass-bin}, the level of the enhancement is independent of galaxy mass with the exception of the highest mass bin, \logm\ $=$ 11.0$-$11.5, which is 0.10$-$0.15 dex higher than the sample average.

The central enhancement to the sSFR falls to zero around 1.2 \reff\ and the outskirts of the galaxies are lightly suppressed by 0.1 dex. As we will show in the next section, \S~\ref{sec:dm}, the offsets seen in the disks of paired galaxies are largely driven by whether the galaxy is the more massive or less massive companion in the pair.

\textbf{To understand why the profiles of high mass galaxies behave differently from the rest of the sample in Figures \ref{fig:ssfr_prof}, \ref{fig:ewha_prof}, and \ref{fig:ssfr_mass}, we compare the distribution of the projected separation for the whole sample and for galaxies in the highest mass bin in Figure \ref{fig:sep_hist}.} The whole sample has a v-shaped separation distribution. This is the result of the combination of the two different samples, the inside-IFU and outside-IFU samples. The outside-IFU sample should find more pairs at wide projected separations due to the larger volume to find companions in. The separation distribution of the inside-IFU sample is limited by MaNGA's IFU sizes and the sample's redshift distribution; the maximum possible projected separation for a MaNGA target with $z$ $=$ 0.15 and a 127 spaxel IFU is about 40 kpc.

The highest mass galaxies in the sample are at closer projected separations in comparison to the rest of the sample with 70\% of the highest mass galaxies being within 20 kpc. \textbf{ The cause of this may be due to clustering effects where high mass galaxies tend to be at the centers of galaxy clusters \citep{Cooray:2002, Zehavi:2002}}. As we will show in \S~\ref{sec:sep}, the central sSFR enhancement is strongest at small projected separation which means that higher sSFR in the centers of the massive galaxies may be driven by their close projected separations.

@@

The mass ratio here is defined as, 
\begin{equation}\label{eq:dm}
\Delta {\rm log}(M) = {\rm log}(M_{\rm target}) - {\rm log}(M_{\rm comp}),
\end{equation}
where $M_{\rm target}$ is the stellar mass of the MaNGA target galaxy and $M_{\rm comp}$ is the stellar mass of \textbf{its identified} companion galaxy. \textbf{In the inside-IFU sample, we have stellar masses for the MaNGA target galaxy but not the other identified pairs. Because of this, we leave the inside-IFU companions out of this analysis.}

\textbf{In the top left of Figure \ref{fig:ssfr_dm}, we split difference profiles into four mass ratio bins from $|\Delta$log(M)$|$ $=$ 0.0$-$1.0. Here, $|\Delta$log(M)$|$ $\le$ 0.5, represents equal mass major mergers while $|\Delta$log(M)$|$ $\ge$ 0.5 represents minor mergers. We see that there is a clear preference for pairs in major merger to have higher sSFR enhancements in their centers, $\sim$0.4 dex, while minor mergers show a weaker sSFR enhancement of $\sim$0.0$-$0.2 dex. The effect can be seen more clearly with the data extracted from the central 0.5 \reff\ in the top right panel. Here the $\Delta$log(sSFR) falls linearly with wider mass ratios, reaching zero enhancement to the sSFR at $|\Delta$log(M)$|$ $=$ 1.5$-$1.75.}

\textbf{We not only use the mass ratio to study how a major merger behaves differently from a minor merger but also to study how the more massive galaxy of a pair behaves differently from the less massive galaxy of the pair. We expect that either component of a similar mass pair will behave in a similar fashion; however, in a minor merger the large central galaxy may not respond to the merger event in the same way as its less massive companion. The two different scenarios can be differentiated with our definition of the mass ratio in equation \ref{eq:dm}; when the MaNGA target is the more massive companion of the pair, its mass ratio is positive and when MaNGA target is the less massive companion of pair the mass ratio is negative. To distinguish between these scenarios, we refer to the more massive galaxy of a pair as the primary companion and the less massive galaxy of a pair the secondary companion.}

In \textbf{bottom left panel} of Figure \ref{fig:ssfr_dm}, we split the profiles by mass ratio in four bins. \textbf{The primary companions are the pairs with $\Delta$log(M) $\ge$ 0.0 and the secondary companions are the pairs with $\Delta$log(M) $\le$ 0.0. When splitting the mass ratio like this we see that major mergers still higher levels of sSFR enhancement in comparison to minor mergers; however, we also see that the less massive companion of the pair sees a higher $\Delta$log(sSFR) in comparison to the more massive companion of a pair. In major mergers, the sSFR enhancement is $\sim$0.2 dex higher in secondary companions in comparison to primary companions and in minor mergers the sSFR enhancement is $\sim$0.1 dex higher in secondary companions in comparison to primary companions.}

In \textbf{bottom right panel} of Figure \ref{fig:ssfr_dm} we see that the sSFR enhancement is strongest in galaxies close to a 1:1 mass ratio ($\Delta$log($M$) $=$ 0.0). These galaxies feature a central enhancement of $\sim$0.35 dex which is 0.1 dex higher than the average central enhancement of the whole sample. This enhancement falls with wider mass ratio; however, pairs with large differences in stellar mass still feature substantial levels of star formation enhancement, 0.15$-$0.20 dex at mass ratios of $|\Delta$log($M$)$|$ $=$ 1.0. We also see that secondary companions show a higher level of sSFR enhancement, by $\sim$0.1 dex, with respect to primary companions.

\textbf{We also see that the $\Delta$log(sSFR) in the outskirts ($R$ $>$ 1.5 \reff) of the pairs have a dependence on the mass ratio in the bottom right of Figure \ref{fig:ssfr_dm}. Primary companions show a zero to positive enhancement of 0.0$-$0.4 dex to the sSFR in their outskirts, while secondary companions feature a suppression to the sSFR in their outskirts of about 0.0$-$0.4 dex. Again we note that only 37\% of the MaNGA sample is designed to extend beyond 1.5 \reff; however, a similar result has been observed in the hydrodynamical simulations of \citet{Moreno:2015}. }

@@

This effect can be seen more clearly in the plot of the central $\Delta$log(sSFR) enhancement as a function of projected separation. The level of the enhancement gradually increases with closer separation from 50 kpc to 10 kpc. While $\Delta$log(sSFR) falls at higher separations, there is still a substantial level of enhancement between 40 and 50 kpc, $\sim$0.1$-$0.2 dex. Within 20 kpc, the $\Delta$log(sSFR) enhancement jumps to 0.3$-$0.4 dex. Our data shows that the sSFR enhancement persists out to at least $r_{\rm p} = 50$~kpc, which is the limit of our pair selection.

\textbf{There is also v-shaped dip in the data at 30$-$40 kpc. The dip is partially due to the mixing of the inside-IFU and outside-IFU samples. If we mask out the inside-IFU pairs, the $\Delta$log(sSFR) over projected separation curve becomes smoother; however, a weak dip still exist at 30$-$40 kpc. In the next section, we will compare our results with those from previous studies.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}\label{sec:disc}

\section{Physical Scenario}

\subsection{Comparison with Previous Work}

\subsubsection{Radial Difference Profiles}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=3in]{fig/prof_comp.pdf}
\caption[]{The mean radial profile of $\Delta$log(sSFR) (\textbf{Top}) and $\Delta$log(SFR) (\textbf{Bottom}) between pairs and controls of this work with the tailored control method ({\it Black}) compared against those of \citet{Pan:2019} ({\it Red}), a pair sample, and \citet{Thorp:2019} ({\it Blue}), a post-merger sample.}
\label{fig:prof_comp}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In Figure \ref{fig:prof_comp} we compare the $\Delta$log(sSFR) profile \textbf{and $\Delta$log(SFR)} as a function of galactocentric radius between our work and previous works. \textbf{\citet{Thorp:2019} studies a sample of 36 post-mergers from the MaNGA sample. The centers of the post-merger galaxies feature a greater level of sSFR enhancement in their centers compared to our galaxies pairs of $\Delta$log(SFR) $=$ 0.40$-$0.45, roughly 0.2 dex higher than our paired galaxies. Between 0.4$-$1.0\reff\ the post-merger galaxies and our pairs are in closer agreement, being 0.05$-$0.1 dex higher than our paired galaxies. Beyond 1.0 \reff\ the post-merger galaxies have a higher $\Delta$log(SFR) by about 0.1$-$0.2 dex.} The heightened level of sSFR enhancement in the centers of post-merger galaxies in comparison to merging galaxies seems consistent with the idea that a second and greater burst of star formation occurs as the two merging galaxies coalesce into a single galaxy.

\textbf{\citet{Pan:2019} studies a set of 205 paired galaxies in the MaNGA sample, focusing on the sSFR enhancement as a function of the merger interaction stage. The $\Delta$log(sSFR) profiles of the galaxies pairs in \citet{Pan:2019} are $\sim$0.10$-$0.15 dex above the profiles in our sample.} Our paired galaxies show a slight sSFR suppression in their disks past 1.0 \reff\ while the galaxy pairs in \citet{Pan:2019} show an enhancement of $\sim$0.15 dex to the sSFR in their disks.

The reason for the discrepancies between our samples may be that \citet{Pan:2019} includes a set of \textbf{96 pairs which are too close to be separately de-blended by SDSS, 82 of which are post-merger galaxies. \citet{Pan:2019} shows that pairs with morphological distortions show higher $\Delta$log(SFR) when compared to pairs without morphological distortions. Further, \citet{Thorp:2019} showed that post-merger galaxies have $\Delta$log(SFR) profiles which are higher than our sample's profiles. From this, infer that these 96 morphologically identified close pairs and post-mergers are the primary reason why the $\Delta$log(sSFR) profile from \citet{Pan:2019} is higher than our profile.   }
